\boldmath Distributed Range-Only Localisation that Preserves Sensor and Navigator Privacies\\\normalfont(Formerly: Privacy-Preserving Localization Using Private Linear-Combination Aggregation)

### 2021-06-17 authors_responses/first_tac_rejection/authors_response.tex
Went over and proof read all responses. Updated title to use the new title (and state the former title as well)

\title{\boldmath Privacy-Preserving Localization Using Private Linear-Combination Aggregation}
\subtitle{Response to Reviewers' Comments - Submission IEEE-TAC 20-2108}
\author{Marko Ristic\and Benjamin Noack\and Uwe D. Hanebeck}

@@

Thank you for the response. We have undertaken a large overhaul of the manuscript in order to accommodate the suggested changes of the reviewers. The work has been shortened by four pages, the introduction shortened to a single page and the novelty of our method clearly stated within it. We state the estimation problem tackled, namely, a modified EKF estimator for range-only sensor localisation with specific security requirements, and its benefits over existing and comparable approaches. We believe that the more clarified contribution and novelty also better justify the relevance of the paper to the TAC journal.

\item \reviewtext{We encourage you to examine carefully the comments of the enclosed reviews and to consider making a major revision of the paper, which can be resubmitted as a Technical Note, to the Transactions on Automatic Control.  If you do submit a revised version of the paper as a Technical Note, you should take care that the paper is reduced to no
more than 8 double-column pages using IEEE template.

In your letter of transmittal, you should include a detailed "author's response" document describing the changes in the paper and you should refer to the present paper number.

Please login, click on the "Author" link at the bottom of your access page, and upload your technical note under the SAME reference number. A new reference number will be assigned to your revised paper.}

After a large revision of our manuscript, including the suggested additions and modifications from the reviewers, we have rearranged and greatly shortened the work (in particular the introduction and cryptography sections, but all sections have been partially modified to be clearer). Due to the novelty of the tackled problem and the cryptographically backed solution, the manuscript, albeit four pages shorter, is still too long for submission as a Technical Note, and we would like to resubmit the work as a full paper again. We hope that this decision is made clearer from the newly revised and rearranged manuscript. Below, we have detailed how each of the reviewer comments have been taken into account when revising the work.

@@

We understand that the state of the initial submission was not as well suited to the TAC journal as could be desired and thank the reviewer for pointing this out. Existing literature published at TAC and concerning cryptographic constructs (for example, ``Cloud-based quadratic optimization with partially homomorphic encryption'' by Andreea Alexandru et al.), has been used as reference during our revision. For the resubmission, we have greatly reduced the cryptographic components of the work and stated our contribution and its novelty more clearly to clarify the suitability of the proposed estimation method to the TAC journal. We will additionally consider some of the heavier cryptographic computations presented for an alternative submission elsewhere.

@@

As above, we regret that the quantity of presented cryptographic content was so poorly suited to the context of TAC and have greatly modified the work to make it a better fit. Much of the cryptographic discussion has been removed and the remaining, necessary but dense, novel notions have been put in the appendix. We hope this makes the work better suited in the context of TAC.

@@

We're happy to hear that the results were found interesting and regret that the length and organisation have made the manuscript hard to read. We have heavily reorganised and rewritten parts of the work to make it easier to follow, including shortening the work by four pages. We hope that the flow of information is now easier to follow and that the method is more concisely described.

@@

We're sorry that the introduction was found too long and agree that it could be made shorter. We have now greatly reduced the length of the introduction and removed a lot of the cryptographic reminders throughout the work. We hope that the new layout is easier to read and follow.

@@

We're glad to hear that the contribution was found interesting and important. We have made a very large revision of the work, including rewriting, reorganising and shortening the text to make the information easier to follow.

@@

Estimating the second moment of the system noise, $\mat{Q}$, is the standard procedure when using linearising filters such as the EKF (see, for example, ``Bayesian Estimation and Tracking: A Practical Guide'' by Anton J. Huag), and is specific to the system being modelled. As it is possible to use a different, non-linearising, filter for the prediction step of the algorithm, it is possible to avoid having to compute $\mat{Q}$, but as we have stated above, we have presented the EKF equations for state prediction where computing it would be necassary.

>>>>

\title{\boldmath Distributed Range-Only Localisation that Preserves Sensor and Navigator Privacies\\\normalfont(Formerly: Privacy-Preserving Localization Using Private Linear-Combination Aggregation)}
\subtitle{Response to Reviewers' Comments - Submission IEEE-TAC 20-2108}
\author{Marko Ristic\and Benjamin Noack\and Uwe D. Hanebeck}

@@

Thank you for the response. We have undertaken a large overhaul of the manuscript in order to accommodate the suggested changes of the reviewers. The work has been shortened by four pages, the introduction shortened to a single page and the novelty of our method clearly stated within it. We state the estimation problem tackled, namely, a modified EKF estimator for range-only sensor localisation with specific security requirements, and its benefits over existing and comparable approaches. We believe that the clearer novelty and contribution also better clarify the relevance of the paper to the TAC journal.

\item \reviewtext{We encourage you to examine carefully the comments of the enclosed reviews and to consider making a major revision of the paper, which can be resubmitted as a Technical Note, to the Transactions on Automatic Control.  If you do submit a revised version of the paper as a Technical Note, you should take care that the paper is reduced to no
more than 8 double-column pages using IEEE template.}

After a large revision of our manuscript, including the suggested additions and modifications from the reviewers, we have rearranged and greatly shortened the work (in particular the introduction and cryptography sections, but all sections have been partially modified to be clearer). Due to the novelty of the tackled problem and the cryptographically backed solution, the manuscript, albeit four pages shorter, is still too long for submission as a Technical Note, and we would like to resubmit the work as a full paper again. We hope that this reasoning is made clearer in the newly revised and rearranged manuscript. Below, we have detailed how each of the reviewer comments has been taken into account when revising the work.

@@

We understand that the state of the initial submission was not as well suited to the TAC journal as could be desired and thank the reviewer for pointing this out. Existing literature published at TAC and concerning cryptographic constructs (for example, ``Cloud-based quadratic optimization with partially homomorphic encryption'' by Andreea Alexandru et al.), has been used as a reference during our revision. For the resubmission, we have greatly reduced the cryptographic components of the work and stated our contribution and its novelty more clearly to clarify the suitability of the proposed estimation method to the TAC journal. We will also consider some of the denser cryptographic definitions presented for an alternative submission elsewhere.

@@

As above, we regret that the quantity of presented cryptographic content was overwhelming and have greatly modified the work to make it more suitable for the journal. Much of the cryptographic discussion has been removed and the remaining necessary novel notions have been put in the appendix.

@@

We're happy to hear that the results were found interesting and regret that the length and organisation have made the manuscript hard to read. We have heavily reorganised and rewritten parts of the work to make it easier to read, including shortening the work by four pages. We hope that the flow of information is now easier to follow and that the method is more concisely described.

@@

We agree with the reviewer that the introduction could be made shorter. We have now significantly reduced the length of the introduction and removed a lot of the cryptographic reminders throughout the work.

@@

We're glad to hear that the contribution was found interesting and important. We have made a very large revision of the work, including rewriting, reorganising and shortening the text to make the presented information easier to follow.

@@

Estimating the second moment of the system noise, $\mat{Q}$, is a standard requirement when using linearising filters such as the EKF (see, for example, ``Bayesian Estimation and Tracking: A Practical Guide'' by Anton J. Huag). This can be done in various ways specific to the system being modelled and is beyond the scope of this work. As it is possible to use a different, non-linearising, filter for the prediction step of the algorithm, it is possible to avoid having to compute $\mat{Q}$, but as we have used the EKF equations for state prediction, computing it would be necessary.
